--- 
title: "Anwendung 1: Histogramm" 
author: "Dirk Seidensticker/Clemens Schmid" 
date: "6. Februar 2016" 
---

# Anwendung 1: Histogramm

ggplot2 und die Daten laden:
```{r} 
library(ggplot2)
```

```{r} 
df <- read.csv("downloads/r-tut/data/AtlantPottery.csv", sep = '\t')
```

```{r, echo=FALSE} 
as.factor(df$size) -> df$size
as.factor(df$vesselShape) -> df$vesselShape
df$feature_simple <- as.factor(ifelse(df$feature != "surface", "excavation", "surface"))
```

# Anwendung 1: Histogramm

Einfaches Histogramm

```{r, message=FALSE, fig.width=10, fig.height=6} 
ggplot(df, aes(wt)) + 
  geom_histogram()
```

# Anwendung 1: Histogramm

Kategoriebreite anpassen

```{r, fig.width=10, fig.height=6} 
ggplot(df, aes(wt)) + 
  geom_histogram(binwidth = 100)
```


# Anwendung 1: Histogramm

Bildausschnitt anpassen

```{r, fig.width=10, fig.height=5} 
ggplot(df, aes(wt)) + 
  geom_histogram(binwidth = 25) + 
  xlim(0, 1000)
```

# Anwendung 1: Histogramm

Gefülltes Balkendiagramm

```{r, fig.width=10, fig.height=5} 
ggplot(df, aes(wt, fill = sherd)) + 
  geom_histogram(binwidth = 25) + 
  xlim(0, 1000)
```

# Anwendung 1: Histogramm

Alternative Ansicht

```{r, fig.width=10, fig.height=5.5} 
ggplot(df, aes(wt, fill = sherd)) + 
  geom_histogram(binwidth = 25) + 
  xlim(0, 1000) +
  theme_bw()
```


# Anwendung 1: Histogramm

Achsenbeschriftung

```{r, fig.width=10, fig.height=5} 
ggplot(df, aes(wt, fill = sherd)) + 
  geom_histogram(binwidth = 25) + 
  xlim(0, 1000) + 
  xlab("Gewicht [g]") +
  ylab("Anzahl")
```

# Anwendung 1: Histogramm

Titel und Position der Legende

```{r, fig.width=10, fig.height=4.75} 
ggplot(df, aes(wt, fill = sherd)) + 
  geom_histogram(binwidth = 25) + 
  xlim(0, 1000) + 
  xlab("Gewicht [g]") +
  ylab("Anzahl") + 
  theme(legend.position = c(1,1), legend.justification = c(1,1))
```
