---
title: "ISAAKiel"
output:
  html_document:
    css: frontpage_styles.css
    theme: "spacelab"
    includes:
      in_header: elements/header.html
    self_contained: no
    smart: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

<style type = "text/css">
.main-container {
  max-width: none;
}
</style>

<div class="row row-striped">
<div class="col-md-8 col-md-offset-2">

## Scope

Archaeoinformatics, computational archaeology and quantitative methods have been a constant and developing branch for the last decades. It comprises different aspects of archaeology and information technology in daily work as well as methodology. Both - the use of the current technology and the methodological implementation in archaeology - have to be developed. This is the aim of our working group **ISAAK** (**I**nitiative for **S**tatistical **A**nalysis in **A**rchaeology **K**iel).

</div>
</div>
<div class="row row-striped">
<div class="col-md-8 col-md-offset-2">

## Who we are

We are archaeologists developing IT solutions and statistical tools in and for our work actively involved in the following institutions:

* [Institut für Ur- und Frühgeschichte, Christian-Albrechts-Universität zu Kiel](https://www.ufg.uni-kiel.de/)
* [Niedersächsisches Institut für historische Küstenforschung, Wilhelmshaven](http://www.nihk.de/)
* [Institut für Archäologische Wissenschaften Bern](http://www.iaw.unibe.ch)
* [Max Planck Institute for Evolutionary Anthropology](https://www.eva.mpg.de)

```{r echo = FALSE, message = FALSE}
#### load api functions and api key ####
source("R/github_api_conv.R")
load("oauth.RData")

#### get org members info from github api ####
members_info <- api_call("https://api.github.com/orgs/ISAAKiel/public_members", "login", oauth)

#### call single users ####
user_info <- list()
for (i in 1:nrow(members_info)){
  #user_res <- content(GET(paste("https://api.github.com/users/", members_info$login[i], sep = "")))
  user_res <- content(GET(paste(
    "https://api.github.com/users/", members_info$login[i],
    sep = ""
  ), add_headers(Authorization = paste("token", oauth))))
  user_info[[i]] <- user_res
}

#### transform single users list to a nice data.frame ####
user_info <- api_trans(user_info, "login")

#### sort users data.frame ####
user_info <- user_info[order(user_info$name), ]

#### get list of active members to split user list ####
active_members <- readr::read_csv("data/active_members_list.csv")
user_info_active <- dplyr::semi_join(user_info, active_members, by = c("login" = "github_login"))
user_info_alumni <- dplyr::anti_join(user_info, active_members, by = c("login" = "github_login"))

#### function to prepare html for user files ####
prepare_user_tiles <- function(user_info, col_setting) {
  for (i in 1:nrow(user_info)){
    cat('<div class="col-xs-6 col-sm-2">')
    cat('<div class="card">')
    # show users avatar
    user_avatar_string <- paste(
      '<a class="img-card" href="', user_info$html_url[i], '" target="_blank" >
       <img src="', user_info$avatar_url[i], '" />
       </a>'
    )
    cat(user_avatar_string, "<br/>")
    cat('<div class="card-content"><h4 class="card-title">')
    # show real name if available - otherwise show login
    if (!is.na(user_info$name[i])){
      name_string <- user_info$name[i]
    } else {
      name_string <- user_info$login[i]
    }
    cat(
      '<a href="', user_info$html_url[i],'" style="color:#345578;" target="_blank">',
      name_string,
      "</a></h4><br/>"
    )
    cat('</div>')
    cat('</div>')
    cat('</div>')
  }
}
```

<div class="row">
```{r results = 'asis', echo = FALSE}
prepare_user_tiles(user_info_active)
```
</div>

</div>
</div>
<div class="row row-striped">
<div class="col-md-8 col-md-offset-2">

## What we do and offer:

We offer programs, scripts and functions for data management and interoperability, develop R-packages for different tasks and present tutorials for programs and archaeological tasks. Everything in constant development and freely accessible in our github repository.

Currently we work on this topics:

* statistical and quantitative methods
* spatial analysis
* data bases and data management
* mapping and remote sensing
* simulation and reconstruction
* open data and open publishing

To see our current portfolio, visit the [projects](projects.html) page.

</div>
</div>
<div class="row row-striped">
<div class="col-md-8 col-md-offset-2">

## Would you like to participate?

Feel free to [fork][fork] a repository, submit an [issue][issue], or contact us, if you are interested to join our group.

[fork]: http://help.github.com/fork-a-repo/
[issue]: https://help.github.com/articles/creating-an-issue/

</div>  
</div>  
<div class="row row-striped">
<div class="col-md-8 col-md-offset-2">

## Alumni

```{r results = 'asis', echo = FALSE}
prepare_user_tiles(user_info_alumni)
```
</div>
</div>
